Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-11 index.Rmd
moved note

`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**  
--

@@

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates. However, as with any real-world intervention, scientific reform can have unintended consequences. Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom.

>>>>

`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. The multi-analyst approach comes with many worthy uses, from demonstrating the arbitrariness and impact of individual analytic choices to acknowledging the inherent variability of results and averaging across idiosyncratic analytic choices to obtain more accurate parameter estimates. However, as with any real-world intervention, scientific reform can have unintended consequences. Here, we focus on the effects of crowdsourcing data analysis, and find that the multi-analyst approach may have an unintended consequence.
While partly instituted with the goal of improving the credibility of scientific research (as shown in Table 1), lay consumers appear to resist the variability and lack of consensus that often comes with multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error and experimenter degrees of freedom. Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies. 
--

@@
